---
title: "PA1_template.md"
output: html_document
---

First step is loading and preprocessing the data.

```{r, echo=TRUE}
data<- read.csv("activity.csv")

```
Calculate the total number of steps taken per day (ignore the missing values in the dataset).

```{r, echo=TRUE}
mydata<-na.omit(data) 
steps<-aggregate(mydata$steps, by=list(mydata$date),FUN="sum")
names(steps)<-c("Date", "Sum of Steps")
print(steps)
```
Make a histogram of the total number of steps taken each day.
```{r, echo=TRUE}
hist(as.numeric(steps$"Sum of Steps"))
```





Calculate and report the mean and median of the total number of steps taken per day. 
```{r, echo=TRUE}
mean<- aggregate(mydata$steps, by=list(mydata$date), FUN="mean")
median<- aggregate(mydata$steps, by=list(mydata$date), FUN="median")
names(mean)<- c("date", "mean of steps")
print(mean)
```

Calculate and report the median of the total number of steps taken per day. 
```{r, echo=TRUE}
median<- aggregate(mydata$steps, by=list(mydata$date), FUN="median")
names(median)<- c("date", "median of steps")
print(median)
```



Make a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis). 

```{r, echo=TRUE}
interval<- aggregate(mydata$steps, by=list(mydata$interval), FUN="mean")
plot(interval$Group.1,interval$x, type="l",
     main="Average number of steps across all days per each interval", 
     xlab="5-minute Intervals (0:00 am to 23:55 pm)",ylab="Average Number of Steps Across all Days")
```






The 8:35 am interval, contains the maximum number of steps on average across all the days in the dataset.
```{r, echo=TRUE}
subset(interval, x==max(interval[,2]), select=Group.1)
```

Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs).
```{r, echo=TRUE}
nas<- nrow(data)-sum(complete.cases(data[,1]))
print(nas)
```

Devise a strategy for filling in all of the missing values in the dataset.
```{r,echo=TRUE}
missing<- merge(data,mean, by="date")

library(dplyr)

replaced<-for(i in 1:nrow(missing))
{  if(is.na(missing[i,2])==TRUE) {
  missing[i,2] <-missing[i,4]}
  else{
    missing[i,2] <- missing[i,2]}
}
```








